---
output: pdf_document
classoption: landscape
sansfont: Calibri Light
header-includes:
   - \usepackage{subcaption,fancyhdr,graphicx,lastpage,hyperref,lmodern}
---

\fontfamily{lmss}\selectfont

```{r echo = FALSE, results = "hide"}
knitr::opts_chunk$set(warning=FALSE, message=FALSE)
```

```{r echo = FALSE}
library(BETS)
has.logo = TRUE
has.email = TRUE
has.website = TRUE 
analist.name = "Terraço Econômico"
analist.email = "terracoeconomico@gmail.com"
analist.site = "www.terracoeconomico.com.br"
```

\def\haslogo{`r as.integer(has.logo)`}
\def\hasemail{`r as.integer(has.email)`} 
\def\haswebsite{`r as.integer(has.website)`} 

\fancypagestyle{plain}{
  \fancyhf{}
  \setlength{\headheight}{45pt} 
  \fancyhead[L]{
    \includegraphics[width=\linewidth,height=40pt]{logo_bets} }
  \fancyhead[R]{
    {\fontfamily{lmss}\selectfont
    {\footnotesize Analysis by} \\
    \ifnum\haslogo = 1
      \includegraphics[width=\linewidth,height=35pt]{logo_terraco} \\
    \else
      `r analist.name` 
    \fi
    \ifnum\haswebsite = 1
      {\small \url{`r analist.site`}}
    \fi
    }
  }
  \fancyfoot[L]{
     {\fontfamily{lmss}\selectfont
     {\small Charts generated by the \textbf{BETS R Package} on `r Sys.Date()` $\diamond$ \textbf{\url{https://github.com/pedrocostaferreira/BETS}}}}
  }
  \fancyfoot[R]{
    \thepage\  / \pageref{LastPage} }
}
\pagestyle{plain}


```{r echo = FALSE, results = "hide"}
BETSchart(alias = "ipca", file = "..\\inst\\ipca", out = "pdf")
```


```{r echo = FALSE, results = "hide"}
BETSchart(alias = "ulc", file = "..\\inst\\ulc", out = "pdf")
```

\begin{figure}[h]
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=1\linewidth]{ipca}
  \label{ipca}
\end{subfigure}
~
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=1\linewidth]{ulc}
  \label{cut}
\end{subfigure}
\end{figure}


```{r, echo = FALSE, results='asis'}
text <- paste(readLines("text.txt"), collapse=" ")
text = gsub(pattern = "\\\\n", replacement = "  \n", x = text)
text <- strsplit(text, "##")[[1]]
cat(text[1])
```

\newpage


