---
classoption: landscape
sansfont: Calibri Light
output:
  rmarkdown::pdf_document:
    includes:  
      in_header: fix_figs.tex
---

\fontfamily{lmss}\selectfont


```{r echo = FALSE}
library(BETS)
```

```{r echo = FALSE, results = "hide"}
knitr::opts_chunk$set(warning=FALSE, message=FALSE)
```

\fancypagestyle{plain}{
  \fancyhf{}%
  \setlength{\headheight}{40pt} 
  \fancyhead[L]{
    \includegraphics[width=\linewidth,height=35pt]{logo_sentiment} }
  \fancyfoot[L]{
     {\fontfamily{lmss}\selectfont
     {\small Charts generated by the \textbf{BETS R Package} on `r Sys.Date()` $\diamond$ \textbf{\url{https://github.com/pedrocostaferreira/BETS}}}}
  }
  \fancyfoot[R]{
    \thepage\  / \pageref{LastPage} }
}
\pagestyle{plain}


```{r echo = FALSE, results = "hide"}
dir.create("graphs")
BETS.chart(ts = "animal_spirits", open = F, file = "graphs//animal_spirits")
BETS.chart(ts = "iie_br", open = F, file = "graphs//iie_br")
BETS.chart(ts = "ei_vars", open = F, file = "graphs//ei_vars")
BETS.chart(ts = "ei_comps", open = F, file = "graphs//ei_comps")
```


\begin{figure}[h]
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=11.5cm,keepaspectratio]{graphs/animal_spirits}
  \label{ipca}
\end{subfigure}
~
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=11.5cm,keepaspectratio]{graphs/ei_vars}
  \label{cut}
\end{subfigure}
~
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=11.5cm,keepaspectratio]{graphs/iie_br}
  \label{cut}
\end{subfigure}
~
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=11.5cm,keepaspectratio]{graphs/ei_comps}
  \label{cut}
\end{subfigure}
\end{figure}


```{r echo = FALSE, results = "hide"}
dir.create("graphs")
BETS.chart(ts = "gdp_vars", open = F, file = "graphs//gdp_vars")
BETS.chart(ts = "gdp_comps", open = F, file = "graphs//gdp_comps")
BETS.chart(ts = "gdp_unemp", open = F, file = "graphs//gdp_unemp")
BETS.chart(ts = "misery_index", open = F, file = "graphs//misery_index")
```


\begin{figure}[h]
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=11.5cm,keepaspectratio]{graphs/gdp_vars}
  \label{ipca}
\end{subfigure}
~
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=11.5cm,keepaspectratio]{graphs/gdp_comps}
  \label{cut}
\end{subfigure}
~
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=11.5cm,keepaspectratio]{graphs/gdp_unemp}
  \label{cut}
\end{subfigure}
~
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=11.5cm,keepaspectratio]{graphs/misery_index}
  \label{cut}
\end{subfigure}
\end{figure}
