---
classoption: landscape
sansfont: Calibri Light
output:
  rmarkdown::pdf_document:
    includes:  
      in_header: fix_figs.tex
---

\fontfamily{lmss}\selectfont


```{r echo = FALSE}
library(BETS)
```

```{r echo = FALSE, results = "hide"}
knitr::opts_chunk$set(warning=FALSE, message=FALSE)
```

\fancypagestyle{plain}{
  \fancyhf{}%
  \setlength{\headheight}{40pt} 
  \fancyhead[L]{
    \includegraphics[width=\linewidth,height=35pt]{logo_sentiment} }
  \fancyfoot[L]{
     {\fontfamily{lmss}\selectfont
     {\small Charts generated by the \textbf{BETS R Package} on `r Sys.Date()` $\diamond$ \textbf{\url{https://github.com/pedrocostaferreira/BETS}}}}
  }
  \fancyfoot[R]{
    \thepage\  / \pageref{LastPage} }
}
\pagestyle{plain}


```{r echo = FALSE, results = "hide"}
dir.create("graphs")
BETS.chart(style = "plotly", alias = "animal_spirits", open = F, file = "graphs//animal_spirits")
```


\begin{figure}[h]
\begin{subfigure}{.49\textwidth}
  \centering
  \includegraphics[width=10.7cm,keepaspectratio]{graphs/animal_spirits}
  \label{ipca}
\end{subfigure}
~
\begin{subfigure}{.49\textwidth}
  \centering
  \includegraphics[width=10.7cm,keepaspectratio]{graphs/animal_spirits}
  \label{cut}
  \caption{Main caption}
\end{subfigure}
~
\begin{subfigure}{.49\textwidth}
  \centering
  \includegraphics[width=10.7cm,keepaspectratio]{graphs/animal_spirits}
  \label{cut}
\end{subfigure}
~
\begin{subfigure}{.49\textwidth}
  \centering
  \includegraphics[width=10.7cm,keepaspectratio]{graphs/animal_spirits}
  \label{cut}
\end{subfigure}
\end{figure}

