---
classoption: landscape
sansfont: Calibri Light
output:
  rmarkdown::pdf_document:
    latex_engine: xelatex
    includes:  
      in_header: fix_figs.tex
---

\fontfamily{lmss}\selectfont

```{r echo = FALSE}
library(BETS)
```

```{r echo = FALSE, results = "hide"}
knitr::opts_chunk$set(warning=FALSE, message=FALSE)
```

\fancypagestyle{plain}{
  \fancyhf{}%
  \setlength{\headheight}{40pt} 
  \fancyhead[L]{
    \includegraphics[width=\linewidth,height=35pt]{logo_sentiment} }
  \fancyfoot[L]{
     {\fontfamily{lmss}\selectfont
     {\small Charts generated by the \textbf{BETS R Package} on `r Sys.Date()` $\diamond$ \textbf{\url{https://github.com/pedrocostaferreira/BETS}}}}
  }
  \fancyfoot[R]{
    \thepage\  / \pageref{LastPage} }
}
\pagestyle{plain}


```{r echo = FALSE, results = "hide"}
dir.create("graphs")
BETS.chart(ts = "animal_spirits", open = F, file = "graphs//animal_spirits")
BETS.chart(ts = "iie_br", open = F, file = "graphs//iie_br")
BETS.chart(ts = "ei_vars", open = F, file = "graphs//ei_vars")
BETS.chart(ts = "ei_comps", open = F, file = "graphs//ei_comps")
```


\begin{figure}[h]
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=11.5cm,keepaspectratio]{graphs/animal_spirits}
  \label{ipca}
\end{subfigure}
~
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=11.5cm,keepaspectratio]{graphs/ei_vars}
  \label{cut}
\end{subfigure}
~
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=11.5cm,keepaspectratio]{graphs/iie_br}
  \label{cut}
\end{subfigure}
~
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=11.5cm,keepaspectratio]{graphs/ei_comps}
  \label{cut}
\end{subfigure}
\end{figure}


```{r echo = FALSE, results = "hide"}
BETS.chart(ts = "gdp_vars", open = F, file = "graphs//gdp_vars")
BETS.chart(ts = "gdp_comps", open = F, file = "graphs//gdp_comps")
BETS.chart(ts = "gdp_unemp", open = F, file = "graphs//gdp_unemp")
BETS.chart(ts = "misery_index", open = F, file = "graphs//misery_index")
```


\begin{figure}[h]
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=11.5cm,keepaspectratio]{graphs/gdp_vars}
  \label{ipca}
\end{subfigure}
~
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=11.5cm,keepaspectratio]{graphs/gdp_comps}
  \label{cut}
\end{subfigure}
~
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=11.5cm,keepaspectratio]{graphs/gdp_unemp}
  \label{cut}
\end{subfigure}
~
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=11.5cm,keepaspectratio]{graphs/misery_index}
  \label{cut}
\end{subfigure}
\end{figure}

```{r echo = FALSE, results = "hide"}
BETS.chart(ts = "conf_lvl", open = F, file = "graphs//conf_lvl")
BETS.chart(ts = "lab_mrkt", open = F, file = "graphs//lab_mrkt")
BETS.chart(ts = "cap_utl", open = F, file = "graphs//cap_utl")
BETS.chart(ts = "transf_ind", open = F, file = "graphs//transf_ind")
```


\begin{figure}[h]
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=11.5cm,keepaspectratio]{graphs/conf_lvl}
  \label{ipca}
\end{subfigure}
~
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=11.5cm,keepaspectratio]{graphs/lab_mrkt}
  \label{cut}
\end{subfigure}
~
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=11.5cm,keepaspectratio]{graphs/cap_utl}
  \label{cut}
\end{subfigure}
~
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=11.5cm,keepaspectratio]{graphs/transf_ind}
  \label{cut}
\end{subfigure}
\end{figure}


```{r echo = FALSE, results = "hide"}
BETS.chart(ts = "servc", open = F, file = "graphs//servc")
BETS.chart(ts = "retail", open = F, file = "graphs//retail")
BETS.chart(ts = "constr", open = F, file = "graphs//constr")
BETS.chart(ts = "consm", open = F, file = "graphs//consm")
```


\begin{figure}[h]
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=11.5cm,keepaspectratio]{graphs/servc}
  \label{ipca}
\end{subfigure}
~
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=11.5cm,keepaspectratio]{graphs/retail}
  \label{cut}
\end{subfigure}
~
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=11.5cm,keepaspectratio]{graphs/constr}
  \label{cut}
\end{subfigure}
~
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=11.5cm,keepaspectratio]{graphs/consm}
  \label{cut}
\end{subfigure}
\end{figure}


## Notes:

Shaded areas represent recessions, as dated by CODACE (FGV/IBRE).

### Animal Spirits

Originally presented by *Bráulio Borges* (researcher, FGV/IBRE).
**Definition**: Average between industry expectations index and consumers expectations index minus the average between industry present situation index and consumers present situation index.
**Source**: FGV/IBRE and Fecomercio-SP

### Misery Index

**Definition**: Inflation rate (IPCA) plus Unemployment Rate (from PNAD-C)
**Source**: IBGE

### Enterprises Confidence Index

**Definition**: Average between industry, services, construction and retail confidence indexes.
**Source**: FGV/IBRE


